Numerical Stability of Detonations in White Dwarf Simulations

### 2018-07-10 papers/ignition/paper.tex
Rename to aastex60
Update to aastex62

\documentclass[twocolumn,numberedappendix]{../aastex6}

@@

\author{Max P. Katz\altaffilmark{1,2}}
\author{Michael Zingale\altaffilmark{2}}

\altaffiltext{1}
{
  NVIDIA Corporation
  2788 San Tomas Expressway
  Santa Clara, CA, 95051, USA
}

\altaffiltext{2}
{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA
}

>>>>

\documentclass[twocolumn,numberedappendix]{../aastex62}

@@

\author{Max P. Katz}
\affiliation
{
  NVIDIA Corporation \\
  2788 San Tomas Expressway, Santa Clara, CA, 95051, USA
}
\affiliation
{
  Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY, 11794-3800, USA
}

\author{Michael Zingale}
\affiliation
{
  Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY, 11794-3800, USA
}
